---
title: "Summer Session II 2022"
output: 
  html_document:
    css: "style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE
)
```

```{r load libraries}
library(fontawesome)
```

This course will provide an introduction to fundamental statistics concepts. Statistical methods will be discussed with an emphasis on data-based critical thinking and decision making. Key to statistics is the ability to clearly convey findings in context, including uncertainty. Using statistics to learn from data is necessary for nearly every field.

<br/> <br/>
<center> <h1> Learning objectives </h1> </center>
Upon successful completion of the course, students should be able to:
identify basic patterns and limitations of empirical data
conduct hypothesis tests for population parameters
check model assumptions
evaluate the significance of their findings and the strength of the evidence
present their analysis and findings in context without statistical jargon


<br/> <br/>
<center> <h1> Typical Weekly Schedule </h1> </center>

## Monday  

- Catalina's office hour 10 - 11am on Zoom (class Zoom link on Canvas)
- Lecture video quiz due on Gradescope at 11:59pm on 

## Tuesday  

- In person lecture 1 - 3:50pm in ICS 180
- HW due on Gradescope at 11:59pm

## Wednesday  

- In person discussion 4 - 4:50pm in DBH 1500
    - Discussion quiz
- Lecture video quiz due on Gradescope at 11:59pm on 

## Thursday  

- In person lecture 1 - 3:50pm in ICS 180
- HW released

## Friday  

- Roy's office hour 3 - 4pm on Zoom (class Zoom link on Canvas)
